Coherent optical association of a single molecule

### 2020-10-24 paper.tex
Update result discussion order

Guided by coupled channel calculations,
we locate the Raman resonance for the atom to molecule transition at
$770.571504(85) ~\mathrm{MHz}$ (Fig.~\ref{f-lifetime}A)
with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$
which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step,
so successful transfer of the atoms to the molecular state will be detected as loss of atoms
in the post experiment image when compared to the initial image.
We observed a Fourier limited linewidth which is evidence of a coherent transfer.
In order to verify the coherence of the transfer directly,
we fix the two photon detuning on resonance and scan the pulse time.
Fig.~\ref{f-raman}C shows the observed Rabi oscillation between the atomic and molecular states.
Fitting the data with a decaying Rabi oscillation suggests that
$69\%$ of initial ground state atoms are transferred into the molecular state.

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the molecular state (Fig.~\ref{f-lifetime}A). We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B) without turning on the second frequency. The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) ~\mathrm{kHz}$. The molecule we form has a lifetime of $0.1990(90) ~\mathrm{ms}$ which is the main limitation on the fidelity of the transfer. The molecule lifetime can be measured directly by preparing the molecule with a $\pi $ pulse and then using a second $\pi $ pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C). The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{fig4.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
    and follows $1/\Delta$ with an offset.
    The fit also includes a small term that is proportional to $P_{tweezer}^2$
    which is caused by the effective magnetic field generated by the tweezer which is
    perpendicular to the real magnetic field.
    (B) Raman Rabi frequency ($\Omega_R$) scales as $P_{tweezer}^{1.29}$
    and follows $1/\Delta$ with an offset.
    From these results we can confirm the theory prediction of
    the atom-molecule matrix element ratio.
    \label{f-det}}
\end{figure*}

@@

%%%% Maybe this following section about the B field can be relegated to a figure caption?
% Figure () shows the geometry of the experiment setup. A $8.8\mathrm{G}$ B field was used to defines the quantization axis in the experiment and is applied perpendicular to the tweezer axis. The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
B field dependency $42.17(24) kHz/G$.

>>>>

Guided by coupled channel calculations,
we locate the Raman resonance for the atom to molecule transition at
$770.571504(85) ~\mathrm{MHz}$ (Fig.~\ref{f-raman}C inset)
with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$
which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step,
so successful transfer of the atoms to the molecular state will be detected as loss of atoms
in the post experiment image when compared to the initial image.
We observed a Fourier limited linewidth which is evidence of a coherent transfer.
In order to verify the coherence of the transfer directly,
we fix the two photon detuning on resonance and scan the pulse time.
Fig.~\ref{f-raman}C shows the observed Rabi oscillation between the atomic and molecular states.
Fitting the data with a decaying Rabi oscillation suggests that
$69\%$ of initial ground state atoms are transferred into the molecular state.
This transfer efficiency is mainly limited by the molecular lifetime
which can be measured directly by preparing the molecule with a $\pi $ pulse
and then using a second $\pi$ pulse to dissociate the molecule back to atoms
after a variable wait time (Fig.~\ref{f-lifetime}A).
The result shows a molecular lifetime of $0.1990(90) \mathrm{ms}$
consistent with the decay of Rabi oscillation.
We obtain the Raman Rabi frequency by fitting our measurements to a model
that includes a Raman Rabi frequency and
a finite lifetime for the molecular state (Fig.~\ref{f-raman}C and inset).
We account for the effect of atomic state loss by measuring the single and
two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B)
without turning on the second frequency.
The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) ~\mathrm{kHz}$.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{fig4.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6\mathrm{GHz}$.
    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
    and follows $1/\Delta$ with an offset.
    The fit also includes a small term that is proportional to $P_{tweezer}^2$
    which is caused by the effective magnetic field generated by the tweezer which is
    perpendicular to the real magnetic field.
    (B) Raman Rabi frequency ($\Omega_R$) scales as $P_{tweezer}^{1.29}$
    and follows $1/\Delta$ with an offset.
    From these results we can confirm the theory prediction of
    the atom-molecule matrix element ratio.
    Insets for (A) and (B), light shift and Raman Rabi frequency on a log-log plot
    showing the power law scaling.
    \label{f-det}}
\end{figure*}

@@

%%%% Maybe this following section about the B field can be relegated to a figure caption?
% Figure () shows the geometry of the experiment setup. A $8.8\mathrm{G}$ B field was used to defines the quantization axis in the experiment and is applied perpendicular to the tweezer axis. The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
\todo{}B field dependency $42.17(24) kHz/G$.
